\documentclass[11pt,dvipsnames]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{datetime}
\newdateformat{monthyear}{%
  \monthname[\THEMONTH] \THEYEAR}

\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=.7in]{geometry}




\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\usepackage{multicol}

% Now begins the stuff that I added.
% ----------------------------------

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\bfseries\Large}
\subsectionfont{\rmfamily\mdseries\normalsize\itshape}

\usepackage[usenames, dvipsnames]{color}
\definecolor{mygray}{gray}{0.6}

\usepackage[explicit]{titlesec}% http://ctan.org/pkg/titlesec
\def\Vhrulefill{\leavevmode\leaders\hrule height 0.0ex depth \dimexpr 0.3pt-0.0ex\hfill\kern0pt} %change both #.#ex to change height
\titleformat{\section}{\bfseries\Large}{}{0pt}{#1~\color{mygray}\Vhrulefill}
%\titleformat{\section}{\bfseries\Large}{}{0pt}{\noindent\Vhrulefill~#1~\Vhrulefill}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}


% Make parskips rather than indent with lists.
\usepackage{parskip}
\usepackage{titlesec}
\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{4pt plus 2pt minus 2pt}
\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{4pt plus 2pt minus 2pt}

% Use fontawesome. Note: you'll need TeXLive 2015. Update.
\usepackage{fontawesome}

% Fancyhdr, as I tend to do with these personal documents.
\usepackage{fancyhdr,lastpage}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0.0pt}
\renewcommand{\footrulewidth}{0.0pt}
\lhead{}
\chead{}
\rhead{}
%\lfoot{
\cfoot{\scriptsize Page \space \thepage \space of \space \hypersetup{linkcolor=black}\pageref{LastPage} \linebreak Updated \monthyear\today}
%\cfoot{\scriptsize  Maria Tackett - CV - \thepage }}
%\rfoot{\scriptsize \thepage/{\hypersetup{linkcolor=black}\pageref{LastPage}}}

% Always load hyperref last.
\usepackage{hyperref}
\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref

\hypersetup{unicode=true,
            pdftitle={Maria Tackett:  CV (Curriculum Vitae)},
            pdfauthor={Maria Tackett},
            pdfkeywords={R Markdown, academic CV, template},
            colorlinks=true,
            linkcolor=Maroon,
            citecolor=Blue,
            urlcolor=CornflowerBlue,
            breaklinks=true, bookmarks=true}
\urlstyle{same}  % don't use monospace font for urls

\begin{document}


\centerline{\huge \bf Maria Tackett}

\vspace{2 mm}

\hrule

\vspace{2 mm}
%job title
\moveleft.5\hoffset\centerline{Assistant Professor of the Practice}
%address
\moveleft.5\hoffset\centerline{Duke University}
\moveleft.5\hoffset\centerline{ 
%github
  
%twitter
%  
%phone
 
%email
\faEnvelopeO \hspace{1 mm} \href{mailto:}{\color{black} \href{mailto:maria.tackett@duke.edu}{\nolinkurl{maria.tackett@duke.edu}}} \hspace{1 mm} 
%website
\faGlobe \hspace{1 mm} \href{http://maria-tackett.netlify.app}{\tt maria-tackett.netlify.app}   }


\vspace{2 mm}

\hrule


\hypertarget{education}{%
\section{Education}\label{education}}

\textbf{Ph.D.~in Statistics} \hfill 2018 \linebreak University of
Virginia \hfill

\vspace{8pt}

\textbf{M.S. in Statistics} \hfill 2010 \linebreak University of
Tennessee-Knoxville \hfill \vspace{8pt}

\textbf{B.S. in Mathematics} \hfill 2009 \linebreak University of
Tennessee-Knoxville \hfill

\hypertarget{academic-appointments}{%
\section{Academic Appointments}\label{academic-appointments}}

\textbf{Assistant Professor of the Practice} \hfill 2018 - present\\
Duke University, Department of Statistical Science

\hypertarget{teaching}{%
\section{Teaching}\label{teaching}}

\emph{Duke University}

\begin{itemize}
\item
  STA 199: Introduction to Data Science \& Statistical Thinking \hfill
  \href{sta199-fa21-003.netlify.app}{Fall 2021},
  \href{https://sta199-fa20-002.netlify.app}{Fall 2020},
  \href{https://www2.stat.duke.edu/courses/Fall19/sta199.001/}{Fall
  2019}, \newline\hspace*\{\textbackslash fill\}
  \href{https://www2.stat.duke.edu/courses/Spring19/sta199.001/}{Spring
  2019} \vskip.8\baselineskip
\item
  STA 210: Regression Analysis
  \hfill \href{https://sta210-fa23.netlify.app}{Fall 2023},
  \href{https://sta210-fa22.netlify.app}{Fall 2022},
  \href{https://sta210-fa21.netlify.app}{Fall 2021},
  \href{https://sta210-sp21.netlify.app}{Spring 2021},
  \href{https://sta210-fa20.netlify.app}{Fall 2020},
  \newline \hspace*\{\textbackslash fill\}
  \href{https://www2.stat.duke.edu/courses/Spring20/sta210.001/}{Spring 2020},
  \href{https://www2.stat.duke.edu/courses/Fall19/sta210.001/}{Fall
  2019},
  \href{https://www2.stat.duke.edu/courses/Spring19/sta210.001/}{Spring
  2019},
  \href{https://www2.stat.duke.edu/courses/Fall18/sta210.001/}{Fall
  2018} \hfill \vskip.8\baselineskip
\item
  STA 310: Generalized Linear Models \hfill
  [Spring 2024](\url{https://sta310-sp24.netlify.app}),
  \href{https://sta310-sp24.netlify.app}{Spring 2022}
  \hfill \vskip.9\baselineskip
\end{itemize}

\emph{Workshops}

\begin{itemize}
\item
  \href{https://rstudio-conf-2022.github.io/teach-ds/}{Designing the
  Data Science Classroom}. rstudio::conf(2022). National Harbor, MD.
  July 2022.
\item
  Strengthening Conceptual Understanding in Introductory Statistics:
  Incorporating active and inclusive teaching and learning strategies
  for in-person and virtual settings (6 session series). UT Austin Dana
  Center. June - July 2021.
\end{itemize}

\hypertarget{publications}{%
\section{Publications}\label{publications}}

\hypertarget{publications-peer-reviewed}{%
\subsection{Publications: Peer
Reviewed}\label{publications-peer-reviewed}}

(* indicates undergraduate student)

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \textbf{Tackett, M.} (2023). Three Principles for Modernizing an
  Undergraduate Regression Analysis Course. \emph{Journal of Statistics
  and Data Science Education}, 31(2), 116-127.
  \href{https://doi.org/10.1080/26939169.2023.2165989}{doi.org/10.1080/26939169.2023.2165989}
\item
  Noll, J., \textbf{Tackett, M.} (2023). Insights from DataFest Point to
  New Opportunities for Undergraduate Statistics Courses: Team
  collaborations, Designing Research Questions, and Data Ethics.
  \emph{Teaching Statistics}, 45(S1), S5-S21.
  \href{https://doi.org/10.1111/test.12345}{doi.org/10.1111/test.12345}
\item
  Easter, M., Schramm-Sapyta, N., \textbf{Tackett, M.}, Larsen, I.*,
  Tang, B., Ralph, M.*, Luong, H.* (2023). Reliance on Community
  Emergency Departments by People Ever Detained in Jail: Retrospective
  Cross-Sectional Study. \emph{Journal of Correctional Health Care.}
  \href{https://doi.org/10.1089/jchc.22.02.0011}{doi.org/10.1089/jchc.22.02.0011}
\item
  \textbf{Tackett, M.}, Viel, S., Manturuk, K. (2023). A validation of
  the short-form classroom community scale for undergraduate mathematics
  and statistics students. \emph{Journal of University Teaching \&
  Learning Practice}, 20(1).
  \href{https://doi.org/10.53761/1.20.01.08}{doi.org/10.53761/1.20.01.08}
\item
  Schramm-Sapyta, N., Ralph, M.*, Huynh, L.*, Tang, B., \textbf{Tackett,
  M.}, Easter, M., Larsen, I.* (2023). Relationships between substance
  use disorders, `severe mental illness' and re-arrest in a county
  detention facility: a 4-year follow-up cohort study. \emph{Criminal
  Behaviour \& Mental Health}, 33(3), 185-195.
  \href{https://doi.org/10.1002/cbm.2277}{doi.org/10.1002/cbm.2277}
\item
  Fannin, D., Ellebya, J., \textbf{Tackett, M.}, Minga, J. (2023).
  Intersectionality of race and question asking in women after right
  hemisphere brain damage. \emph{Journal of Speech, Language, and
  Hearing Research}, 66(1), 314-324.
  \href{https://doi.org/10.1044/2022_JSLHR-22-00327}{doi.org/10.1044/2022\_JSLHR-22-00327}
\item
  Beckman, M. D., Çetinkaya-Rundel, M., Horton, N. J., Rundel, C. W.,
  Sullivan, A. J., \textbf{Tackett, M}. (2020). Implementing version
  control with Git and GitHub as a learning objective in statistics and
  data science courses. \emph{Journal of Statistics Education}, 29(1),
  132-144.
  \href{https://doi.org./10.1080/10691898.2020.1848485}{doi.org./10.1080/10691898.2020.1848485}
\item
  Dotson, M., Alvarez, V.*, \textbf{Tackett, M.}, Asturias, G., Leon,
  I., Ramanujam, M. (2020) Design Thinking-Based STEM Learning:
  Preliminary Results on Achieving Scale and Sustainability Through the
  IGNITE Model. \emph{Frontiers in Education}, 5: 14-24.
  \href{https://doi.org/10.3389/feduc.2020.00014}{doi.org/10.3389/feduc.2020.00014}
\end{enumerate}

\hypertarget{publications-other}{%
\subsection{Publications: Other}\label{publications-other}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{11}
\item
  \textbf{Tackett, M.}, \& Çetinkaya-Rundel, M. (2023). Analyzing and
  Recreating Data Visualizations of W.E.B. Du Bois. \emph{CHANCE},
  36(1), 40-47.
  \href{https://doi.org/10.1080/09332480.2023.2179279}{doi.org/10.1080/09332480.2023.2179279}
\item
  \textbf{Tackett, M.} (2022). My ASA Story: Maria Tackett. \emph{Amstat
  News}, 20, 5.
\item
  \textbf{Tackett, M.}, Burbank, K., Canner, J., \& Çetinkaya-Rundel, M.
  (2021). Teaching Courses Focused on Social Good. \emph{CHANCE}, 34(3),
  69-72.
  \href{https://doi.org/10.1080/09332480.2021.1979821}{doi.org/10.1080/09332480.2021.1979821}
\item
  \textbf{Tackett, M.} (2021, January 14).
  \href{https://medium.com/dukeuniversity/a-flipped-classroom-sparks-online-student-engagement-7d6d8bce9694}{\emph{A
  flipped classroom sparks online engagement}}. Duke Covid Diaries
  Series.
\item
  \textbf{Tackett, M.}, \& Çetinkaya-Rundel, M. (2020). COVID-19 Data in
  the Classroom. \emph{CHANCE}, 33(3), 63-66.
  \href{https://doi.org/10.1080/09332480.2020.1820257}{doi.org/10.1080/09332480.2020.1820257}
\item
  \textbf{Tackett, M.} (2020, July 23).
  \href{https://muser.duke.edu/blog/creating-interactive-web-apps-statistics}{\emph{Creating
  Interactive Web Apps for Statistics}}. Duke Musings Blog.
\item
  Çetinkaya-Rundel, M., \& \textbf{Tackett, M.} (2020). From drab to
  fab: Teaching visualization via incremental improvements.
  \emph{CHANCE}, 33(2), 31-41.
  \href{https://doi.org/10.1080/09332480.2020.1754074}{doi.org/10.1080/09332480.2020.1754074}
\item
  Banks, D., \textbf{Tackett, M.} (2020). Bayesian Methods and Forensic
  Evidence. In Banks, D., Kafadar, K., Kaye, D., Tackett, M. (Eds.),
  \emph{Handbook of Forensic Statistics} (pp.~73 - 90), Chapman \& Hall.
\item
  Banks, D., Kafadar, K., Kaye, D., \textbf{Tackett, M.} (Eds.),
  \emph{Handbook of Forensic Statistics}, Chapman \& Hall.
\end{enumerate}

\hypertarget{invited-talks}{%
\section{Invited Talks}\label{invited-talks}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Tackett, M. \emph{Three principles for modernizing an undergraduate
  regression analysis course.} Teaching Statistics Section seminar.
  Royal Statistical Society. Online. February 2024.
\item
  Tackett, M. \emph{Communication as a learning objective in an
  intermediate statistics course.} Teaching and Evaluating Data
  Communication At Scale. Institute for Mathematical and Statistical
  Innovation. Chicago, IL. January 2024.
\item
  Tackett, M. \emph{Teaching intro data science.} Preparing to Teach
  Workshop. George Mason University. August 2022.
\item
  Tackett, M. \emph{Knit, Commit, and Push: Teaching version control in
  undergraduate statistics courses}. Toronto Workshop on
  Reproducibility. Online. February 2022.
\item
  Tackett, M. \emph{Mentoring Undergraduate Research: Creating
  productive experiences and sharing student work}. ASA Mentoring
  Undergraduate Research Panel. Online. February 2022.
\item
  Tackett, M. \emph{Women in Industry and Academia.} FEMMES+ Hacks
  Conference. Online. October 2021. (Panelist)
\item
  Tackett, M. \emph{What a tap class has taught me about teaching
  statistics}. USCOTS. Online. June 2021.
\item
  Tackett, M. \emph{Building Websites in RStudio}. RLadies Baltimore.
  Online. April 2021.
\item
  Tackett, M. \emph{Building Websites in RStudio}. RLadies Amherst.
  Online. March 2021.
\item
  Tackett, M. \emph{Telling stories with data.} Abraham Lincoln High
  School. Online (Philadelphia, PA). January 2021.
\item
  Tackett, M. \emph{Undergraduate research in statistics.}
  \(\text{OURFA}^2\text{M}^2\) Conference. Online. December 2020.
\item
  Tackett, M. \emph{Thinking about lectures in an intro data science
  course}. Toronto Data Workshop. Online (University of Toronto
  Department of Statistical Sciences). December 2020.
\item
  Tackett, M. \emph{Women in Statistics and Computing.} FEMMES Hacks
  Conference. Online. October 2020. (Panelist)
\item
  Tackett, M. \emph{Opportunities in Statistics and Data Science:
  Lightning Talks (Academia, Government, \& NonProfit)}. StatFest.
  Online. September 2020. (Panelist)
\item
  Tackett, M. \emph{Who's Underrepresented? Modeling Undercounts in the
  U.S. Census}. Joint Statistical Meeting. Online. August 2020.
\item
  Tackett, M. \emph{Making remote lectures active and inclusive in a
  large undergraduate course}. Teaching Statistics Teaching and Learning
  Statistics Online. Online (Royal Statistical Society Teaching
  Statistics Special Interest Group). July 2020.
\item
  Tackett, M. \emph{You don't have to be an expert to create something
  meaningful}. rstudio::conf. San Francisco, CA. January 2020.
\item
  Tackett, M. \emph{Reproducible Research - Education and Practice}.
  Duke Center for Data and Visualization Sciences. Durham, NC. November
  2019. (Panelist)
\item
  Tackett, M. \emph{My Journey in Statistics}. FEMMES Hacks Conference.
  Durham, NC. November 2019. (Keynote)
\item
  Tackett, M. \emph{Statistics in Practice}. FOCUS Cluster Dinner Series
  at Duke University: What if? Explaining the Past/Predicting the
  Future. Durham, NC. November 2019.
\item
  Tackett, M. \emph{Beyond the Buzzword: A Look at Data Science in
  Practice and How You Can Be a Part of It}. SAMSI Diversity in Data
  Science and Machine Learning Conference. Washington, DC. October 2019.
  (Plenary talk)
\item
  Tackett, M. \emph{Women in Machine Learning and Data Science}. Duke
  Machine Learning Day. Durham, NC. March 2019. (Panelist)
\item
  Tackett, M. \emph{Women in Industry}. Duke University Business
  Oriented Women Meeting. Durham, NC. September 2018. (Panelist)
\end{enumerate}

\hypertarget{grants-fellowships}{%
\section{Grants \& Fellowships}\label{grants-fellowships}}

National Science Foundation. \emph{Achieving Critical Transformations in
Undergraduate Programs in Mathematics (ACT UP MATH)}, 2022 - 2025, Role:
Duke Site Co-PI, \$237,749.

Duke Trinity Research Enhancement Fund. \emph{Toward a More Sustainable
Culture of Undergraduate Research in Statistical Science}, 2022 - 2023,
\$13,000.

Duke Learning Innovation's Carry the Innovation Forward Fund.
\emph{Building Community and Self-Efficacy Through Inclusive Teaching
Practices}, 2021 - 2023, Role: Co-PI, \$4,616.

Duke Trinity Research Enhancement Fund. \emph{Toward a More Sustainable
Culture of Undergraduate Research in Statistical Science}, 2021 - 2022,
\$11,000.

Duke Bass Connections - Brain \& Society. \emph{Mental Health and the
Justice System in Durham}, 2020 - 2024, Role: Co-PI, \$14,200 each
academic year.

Duke Data+. \emph{Mental Health and the Justice System in Durham}. 2020
- 2024, Role: Co-PI, \$17,500 each year.

Duke Trinity Research Enhancement Fund. \emph{Toward a More Sustainable
Culture of Undergraduate Research in Statistical Science}, 2020 - 2021,
\$3,000.

Duke Learning Innovation Jump Start Grant, 2019.

National Science Foundation. \emph{Collaborative Research: Accelerating
the Pace of Research and Implementation of Writing-to-Learn Pedagogies
Across STEM Disciplines}, 2018 - 2020, Role: Key Faculty.

Duke University Learning Innovation Active Learning Fellows, 2019 -
2020, \$1,000.

University of Virginia Course Design Institute Fellowship, 2016.

\hypertarget{service-to-profession}{%
\section{Service to Profession}\label{service-to-profession}}

\hypertarget{curriculum-development}{%
\subsection{Curriculum development}\label{curriculum-development}}

UT-Austin Dana Center Statistics Curriculum Authoring Group, 2021

UT-Austin Dana Center Statistics Curriculum Advisory Group, 2020

Howard Hughes Medical Institute Data Exploration Course Advisory
Committee, 2020 - 2021

\hypertarget{editorial-service}{%
\subsection{Editorial service}\label{editorial-service}}

\emph{Journal of Statistics Education}, Associate Editor, 2020 - present

\emph{CHANCE} Magazine Statistics Education Column: Taking a Chance in
the Classroom, Editor, 2019 - present

Journal Reviews: \emph{Journal of Statistics Education; Criminology},
\emph{Criminal Justice, Law \& Society}, \emph{Technology Innovations in
Statistics Education}

Book Reviews: Chapman \& Hall

\hypertarget{asa-and-statistics-education}{%
\subsection{ASA and Statistics
Education}\label{asa-and-statistics-education}}

GAISE Revision Steering Committee, 2023 - present

Bill \& Melinda Gates Foundation High School Math Pathways Advisory
Group, 2023 - present

ASA/MAA Joint Committee on Undergraduate Statistics and Data Science
Education, 2022 - present

Bill \& Melinda Gates Foundation Statistics Courseware Advisory Group,
2022 - present

Symposium on Statistics \& Data Science Program Committee, Short Course
Chair, 2022 - 2023

Symposium on Statistics \& Data Science Program Committee, Poster Chair,
2021 - 2022

CAUSE Undergraduate Statistics Project Competition Co-Chair, 2020 - 2023

ASA Section on Statistics and Data Science Education, Communications
Officer, 2020 - 2022

ASA DataFest Steering Committee, 2019 - 2022

CAUSE Undergraduate Statistics Project Competition Judge, 2019

ASA Section on Bayesian Statistical Science Student Paper Competition
Review Committee, 2019

\hypertarget{university-department-service}{%
\section{University \& Department
Service}\label{university-department-service}}

College Advisor, 2022 - present

Library Council, 2021 - present

Women in Research House Course, Faculty Advisor, 2021

A.B. Duke Scholars Program Interviewer, 2021

Statistical Science Anti-Racism Committee, 2021 - present

Trinity Arts \& Sciences Committee on Curriculum, 2019 - 2021

ASA DataFest@Duke Organizer, 2019 - 2022

Master in Interdisciplinary Data Science Admissions Committee, 2020

Statistical Science Undergraduate Curriculum Committee, 2019 - present

Statistical Science Master's Student Advisor, 2019 - present

Duke SPIRE Mentor, 2019 - present

Statistical Science Undergraduate Major Advisor, 2018 - present

Statistical Science Committee on Departmental Code of Conduct, 2019

Females Excelling More in Math, Engineering, \& Science (FEMMES)
Capstone, 2019

Statistical Science Master's Program Admissions Committee, 2019 \& 2021

Duke Datathon Judge, 2018 \& 2021

\hypertarget{advising}{%
\section{Advising}\label{advising}}

\hypertarget{mental-health-and-the-justice-system-in-durham-county-data-bass-connections}{%
\subsection{Mental Health and the Justice System in Durham County (Data+
\& Bass
Connections)}\label{mental-health-and-the-justice-system-in-durham-county-data-bass-connections}}

\begin{multicols}{2}
\begin{itemize}
\item Irene Biju, 2023 - present
\item Foxx Hart, 2023 - present
\item Will Lieber, 2023 - present
\item Jordan Hamelsky, 2022 - present
\item Zoe Svec, 2022 - 2024
\item Andrew Shi, 2022
\item Maya Pandey, 2021 - 2024
\item Brianna Cellini, 2021 - 2022
\item William Feng, 2021 - 2023
\item John Liakos, 2021
\item Isabella Larson, 2020 - 2023
\item Liz Huynh, 2020 - 2023
\item Matthew Ralph, 2020 - 2022
\end{itemize}
\end{multicols}

\hypertarget{undergraduate-thesis-advisees}{%
\subsection{Undergraduate thesis
advisees}\label{undergraduate-thesis-advisees}}

\begin{itemize}
\tightlist
\item
  Naomi Rubin, 2023
\end{itemize}

\hypertarget{undergraduate-thesis-committee}{%
\subsection{Undergraduate thesis
committee}\label{undergraduate-thesis-committee}}

\begin{itemize}
\item Malavi Ravindran, 2021
\item Michael Model, 2020
\item Daniel Levine, 2019
\item Ben Feder, 2019
\item Srini Sunil, 2019
\end{itemize}

\hypertarget{doctoral-thesis-committee}{%
\subsection{Doctoral thesis committee}\label{doctoral-thesis-committee}}

\begin{itemize}
\tightlist
\item
  Meng Xie, 2021
\end{itemize}

\hypertarget{independent-study}{%
\subsection{Independent study}\label{independent-study}}

\begin{itemize}
\item Joe Choo, 2022
\item Larry Chen, 2022
\item Steven Herrera, 2020
\item Caroline Levenson, 2019
\end{itemize}

\hypertarget{other-supervised-research}{%
\subsection{Other supervised research}\label{other-supervised-research}}

\begin{multicols}{2}
\begin{itemize}
\item Garrett Allen, 2022
\item Martin Olarte, 2022
\item Sean Li, 2021
\item Emmanuel Mokel, 2021
\item Shari Tian, 2021
\item Joe Choo, 2020
\item Abbey List, 2020
\item Glenn Morgenstern, 2020
\item Samantha Owusu-Antwi, 2020
\end{itemize}
\end{multicols}

\hypertarget{professional-affiliations}{%
\section{Professional Affiliations}\label{professional-affiliations}}

Mathematical Association of America, 2022 - present

International Statistical Institute, 2022 - present

Caucus for Women in Statistics, 2021 - present

International Society for Bayesian Analysis, 2021 - present

RStudio Certified Instructor, 2020 - present

American Statistical Association, 2017 - present

National Math Alliance, 2019 - present

Center for Statistics and Applications in Forensic Evidence, 2017 - 2019

\end{document}
